Obtain Article Volume

### 2020-10-11 analysis/005_article_volume.Rmd
exclude corrections and withdrawn articles; fix sql to include articles without page numbers

>>>>

### Article volume excluding paratext

```{sql, connection = "con", output.var = "article_volume_para"}
SELECT
        issued_year,
        issn,
        count(distinct(doi)) as articles     
    FROM
        `api-project-764811344545.cr_dump_march_20.els_hybrid_cr`      
    WHERE
        issued_year > 2014 
        and issued_year < 2020     
    AND NOT     regexp_contains(title,'^Author Index$|^Back Cover|^Contents$|^Contents:|^Cover Image|^Cover Picture|^Editorial Board|^Front Cover|^Frontispiece|^Inside Back Cover|^Inside Cover|^Inside Front Cover|^Issue Information|^List of contents|^Masthead|^Title page|^Correction$|^Corrections to|^Corrections$|^Withdrawn')    
    GROUP BY
        issued_year,
        issn
```

```{r}
article_volume_para %>%
  group_by(issued_year) %>%
  summarise(articles = sum(articles)) %>%
  inner_join(els_vol, by = "issued_year") %>%
  mutate(para = n - articles) %>%
  mutate(para / n * 100)
```
backup

```{r}
write_csv(article_volume_para, here::here("data", "article_volume_para.csv"))
```

### Article volume regular issues excluding paratext

```{sql, connection = "con", output.var = "article_volume_regular"}
    SELECT
        issued_year,
        issn,
        count(distinct(doi)) as articles          
    FROM
        `api-project-764811344545.cr_dump_march_20.els_hybrid_cr`           
    WHERE
        issued_year > 2014          
        and issued_year < 2020              
        AND NOT     regexp_contains(title,'^Author Index$|^Back Cover|^Contents$|^Contents:|^Cover Image|^Cover Picture|^Editorial Board|^Front Cover|^Frontispiece|^Inside Back Cover|^Inside Cover|^Inside Front Cover|^Issue Information|^List of contents|^Masthead|^Title page|^Correction$|^Corrections to|^Corrections$|^Withdrawn')          
         AND (NOT regexp_contains(page, '^S') OR page is NULL)
    GROUP BY
        issued_year,
        issn
```

```{r}
article_volume_regular %>%
  group_by(issued_year) %>%
  summarise(articles = sum(articles)) 
```

```{r}
write_csv(article_volume_regular, here::here("data", "article_volume_para_regular.csv"))
```
